Energy and the CES production function

### 2015-08-14 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Deleted unneeded, commented code.

<<Fitted_and_Residuals>>=
filenameResampleCoeffs <- ""
fittedAndResidData <- function(model, id){
  # ******************************************
  # getData doesn't work for lm models that are created for CSP="Adhere to CSP".
  # After we implement specified values for alpha_1, alpha_2, and alpha_3 in our fitting functions, 
  # getData(model) will probably work.
  # At that time, change model$data to getData(model)
}

temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
  df <- data.frame(select(model$data, Year, Country))
  df$fittedExp <- exp(fitted(model)) # exp accounts for the fact that the model was fitted in log space.
  df$ResidualsExp <- resid(model)
  # df$model <- "exp"
  return(df)
}) %>% do.call(rbind, .)

@@

# No longer using this code, because we have a different "reference" model.
# Get the unadjusted, without-energy residuals from models that adhere to the CSP
# and store them in a data frame
# r_unadj_noE_CSP <- filter(temp_data, flavor=="Unadjusted" & energy=="Without energy" & CSP=="Adhere to CSP") %>% 
#   select(Year, Country, Residuals, model)
# colnames(r_unadj_noE_CSP)[colnames(r_unadj_noE_CSP)=="Residuals"] <- "r_unadj_noE"
# Merge to get the unadjusted, without-energy values next to each country, year, and model
# fitted_and_resid_data <- merge(temp_data, r_unadj_noE_CSP)
# Create a column containing ∆r, the difference between a residual value
# and the residual value in the same year for the unadjusted, no-energy case
# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_unadj_noE"]])

# # Get the reference residuals (from the exponential-only models) and store them in a data frame
# r_ref <- filter(temp_data, model=="exp") %>% select(Year, Country, Residuals)
# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
# # Merge to get the reference values in each appropriate row
# fitted_and_resid_data <- merge(temp_data, r_ref)
# # Create a column containing ∆r, the difference between a residual value
# # and the residual value in the same year for the reference case
# fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["r_ref"]])

# Get the reference residuals (from the exponential-only models) and store them in a data frame
# r_ref <- select(temp_data_exp, Year, Country, ResidualsExp)
# colnames(r_ref)[colnames(r_ref)=="Residuals"] <- "r_ref"
# Merge to get the reference values in each appropriate row
# fitted_and_resid_data <- merge(temp_data, r_ref)
# Create a column containing ∆r, the difference between a residual value
# and the residual value in the same year for the reference case
fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])

>>>>

<<Fitted_and_Residuals>>=
temp_data_exp <- leaf_apply(modelsExp, class=c("lm"), f = function(model, id){
  df <- data.frame(select(model$data, Year, Country))
  df$fittedExp <- exp(fitted(model)) # exp accounts for the fact that the model was fitted in log space.
  df$ResidualsExp <- resid(model)
  return(df)
}) %>% do.call(rbind, .)

@@

# Create a column containing ∆r, the difference between a residual value
# and the residual value in the same year for the reference model
fitted_and_resid_data[["Dr"]] <- abs(fitted_and_resid_data[["Residuals"]]) - abs(fitted_and_resid_data[["ResidualsExp"]])
